\ttitle

### 2013-01-30 Chapters/Chapter2.tex
Working on clustering section

>>>>

This section will give an introduction and overview to clustering of data. 
When processing time series of data the line of distinction between 
segmentation and clustering is very fine. This section will introduce 
clustering for the purpose as used in this project.

Data clustering can be used with two different applications, exploratory or 
confirmatory \cite{jain1999data}. In the former, the purpose is to discover 
clusters in a point cloud of data points. Here the cluster is defined as a 
group of homogeneous data points measured by some coherence measure, often a 
distance function with the data points being defined as vectors. The produced 
clusters, which are a representation of the data examined, can be used in the 
latter application to assign new provided data points to a cluster and thereby 
classify them.

Depended on the precise setup, clustering can be used as a successive step 
after or an implementation of temporal segmentation. When temporal 
segmentation is used to create successive coherent data points, clustering can 
be used to recognize the same activities in different points of time. The data 
points provided to the clustering will be some representation of each segment 
and each segment will be labeled with a activity. An other mechanism could be 
to extract features from the raw data points and use these to create clusters 
directly *** [temporal modifications]. Both mechanisms requires the 
exploratory and confirmatory phases.

The exploratory phase roughly consists of the following five steps 
\cite{jain1999data}
\begin{enumerate}
	\item data point representation,
	\item definition of coherence,
	\item grouping data points,
	\item cluster abstraction,
	\item output qualification
\end{enumerate}

The first step is to find a \emph{representation} of the data points and 
clusters, considering the number, type and scale of the features and the 
number of desired classes to cluster in. When dealing with high-dimensional 
data points a \emph{feature selection} can be performed to use only the most 
discriminating features. When the raw features are not useful enough, 
\emph{extraction} can be used to create new synthetic features. *** 
[qualitative versus quantitative/conceptual]

When the data points are represented in a meaningful way, the measure of 
\emph{coherence} between pairs of points must be defined. Often this is 
implemented as the Euclidean 
or Mahalanobis distance when the data points are represented as vectors or 
other similarity measures for conceptual patterns.

The most critical step, the \emph{grouping},

%-------------------

\subsection{Formal definition}

%-------------------

\subsection{Application is research fields}
